\noindent Dear Reviewers and Editors,
\bigskip

Thank you very much for your helpful feedback in the previous round. In this revision, we have tried our best to address the concerns from the reviewers. For your convenience, we are submitting this review response along with our revised manuscript to explain our revisions. In the following, we will first itemize major changes made to the manuscript, and then we will also provide a point-to-point review response to both meta-review and each reviewer.

\bigskip
In this revision, we have primarily made the following changes. For each change, we have assigned a symbol which related to the corresponding review comment.
\begin{enumerate}
  \item (M3) Perform a brief evalutaion on our speed estimation algorithm with a smaller dataset which contains both cell phone data and GPS data. We perform speed estimation on cell phone data and use GPS data as ground truth. 
  \item Add a limitation section that discuss three main limitations of our work:
	\begin{itemize}
    \item (M4) The lack of WiFi data in our analysis.
    \item (M2b, R1-3) The length of our dataset and the limited geographic area.
		\item (M2c) The limitations introduce by coarse-grained location information and irregular time intervals in the dataset.
  \end{itemize}
  \item (M1) Give more description on our dataset.
	\item (R2-1, R4-1) \change{TODO: Revise the motivation of our work.}
  \item (M5) Add additional references.
	\item (R1-4) Add implementation details and environment settings.
	\item Fix several naming and figure issues. \change{remaining change: figure and listing on the same page as text, fig11 and fig12 to relative value}
  \item Carefully proof read to make sure there is no more language or formatting issue.
\end{enumerate}

